Local Group Satellite Alignments in a Cosmological Context: Insights from the Illustris Simulation

### 2016-05-06 paper/ms.tex
title
new plots in draft
new plots in paper

\begin{document}
%=========================================================================
%		FRONT MATTER
%=========================================================================
\title{Satellite allignments in galaxy pairs in the Illustris Simulation}
\author{
  Ver\'onica Arias \thanks{v.arias@uniandes.edu.co}$^{1}$,
  Jaime E. Forero-Romero \thanks{je.forero@uniandes.edu.co}$^{2}$ 
}

@@

@@

\section{Results}
\label{Results}
\begin{figure}
\centering
\includegraphics[width=\hsize]{axratio_dark_bright.pdf}\\
\caption{Axis ratio of luminous satellites versus the axis ratio for
  dark subhalos.}
\label{fig:StreamPlaneOrbit}
\end{figure}

>>>>

\begin{document}
%=========================================================================
%		FRONT MATTER
%=========================================================================
\title{Local Group Satellite Alignments in a Cosmological Context: Insights from the Illustris Simulation}
\author{
  Ver\'onica Arias \thanks{v.arias@uniandes.edu.co}$^{1}$,
  Jaime E. Forero-Romero \thanks{je.forero@uniandes.edu.co}$^{2}$ 
}

@@

\begin{figure}
\centering
\includegraphics[width=\hsize]{axratio_dark_bright.pdf}\\
\caption{Axis ratio of luminous satellites versus the axis ratio for
  dark subhalos.}
\label{fig:StreamPlaneOrbit}
\end{figure}

\begin{figure*}
\centering
\includegraphics[width=0.48\hsize]{significance_full_dark.pdf}
\includegraphics[width=0.48\hsize]{significance_full_bright.pdf}\\
\includegraphics[width=0.48\hsize]{significance_lg_dark.pdf}
\includegraphics[width=0.48\hsize]{significance_lg_bright.pdf}\\
\caption{Significance of alignments.}
\label{fig:significance}
\end{figure*}

\begin{figure}
\centering
\includegraphics[width=\hsize]{r_u_alignment.pdf}\\
\caption{Alignment of the mayor axis with the vector connecting the
  two halos.}
\label{fig:lg_alignment}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\hsize]{plane_width.pdf}\\
\caption{Plane width for the best planes in the luminious and dark cases.}
\label{fig:plane_width}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\hsize]{plane_width_n_dark.pdf}\\
\caption{Plane width as a function of objects used to find the plane.}
\label{fig:plane_width_nobjects}
\end{figure}

\section{Results}
\label{Results}

@@
